\documentclass{homework}

\usepackage{booktabs}
\usepackage{graphicx}

\usepackage{lmodern}
\usepackage{mdframed}
\definecolor{blockquote-border}{RGB}{221,221,221}
\definecolor{blockquote-text}{RGB}{119,119,119}
\newmdenv[rightline=false,bottomline=false,topline=false,linewidth=2pt,linecolor=blockquote-border,skipabove=\parskip]{customblockquote}
\renewenvironment{quote}{\vspace{6pt plus 2pt minus 1pt}\begin{customblockquote}\fontfamily{lmtt}\selectfont\list{}{\rightmargin=0.75em\leftmargin=0.75em}%
\item\relax\color{blockquote-text}\ignorespaces}{\unskip\unskip\endlist\end{customblockquote}}


\Title{Assignment \#4 - Page Rank in Hadoop}
\DueDate{August 9th, 2020}
\ClassName{Distributed Systems and Cloud Computing}
\ClassNumber{CS549WS}
\ClassSection{Summer 2020}
\Instructor{Professor Dominic Duggan}
\Author{Daniel Kadyrov}
\AuthorID{10455680}

\begin{document}

\maketitle

\section{Introduction}

This assignment focuses on implementing a Page Ranking algorithm to sort the most popular Wikipedia pages from a provided previously downloaded set. Changes were made to the files shown in the following section. A test using a graph was performed using Hadoop on a local machine was performed. The Page Ranking script was then used on AWS EMR on 5, 10, and 20 clusters. 

\newpage
\section{Changes within Provided Files}

\subsection{DiffMap1}
\lstinputlisting[language=Java, caption={DiffMap1.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/DiffMap1.java}

\newpage
\subsection{DiffMap2}
\lstinputlisting[language=Java, caption={DiffMap2.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/DiffMap2.java}

\newpage
\subsection{DiffRed1}
\lstinputlisting[language=Java, caption={DiffRed1.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/DiffRed1.java}

\newpage
\subsection{DiffRed2}
\lstinputlisting[language=Java, caption={DiffRed2.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/DiffRed2.java}

\newpage
\subsection{FinMapper}
\lstinputlisting[language=Java, caption={FinMapper.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/FinMapper.java}

\newpage
\subsection{FinReducer}
\lstinputlisting[language=Java, caption={FinReducer.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/FinReducer.java}

\newpage
\subsection{InitMapper}
\lstinputlisting[language=Java, caption={InitMapper.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/InitMapper.java}

\newpage
\subsection{InitReducer}
\lstinputlisting[language=Java, caption={InitReducer.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/InitReducer.java}

\newpage
\subsection{JoinMapper}
\lstinputlisting[language=Java, caption={JoinMapper.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/JoinMapper.java}

\newpage
\subsection{JoinReducer}
\lstinputlisting[language=Java, caption={JoinReducer.java}]{Assignment4-Code/page-rank/src/edu/stevens/cs549/hadoop/pagerank/JoinReducer.java}

\newpage
\section{Running on Local Machine}

\subsection{Graph Files} 

\begin{lstlisting}[caption={sample.txt}]
1: 2 3 
2: 4
3: 1 4 5
4: 
5: 1 4
\end{lstlisting}

\begin{lstlisting}[caption={names.txt}]
1: v1 
2: v2
3: v3
4: v4
5: v5
\end{lstlisting}

\begin{lstlisting}[caption={output.txt}]
4:0	1.708333333333333
1:0	0.8583333333333333
3:0	0.575
2:0	0.575
5:0	0.43333333333333335
\end{lstlisting}

\subsection{Run Tests}

The following command was used to test the local hadoop graph ranking algorithm. 

\begin{lstlisting}[language=Bash, caption={Local Command}]
edu.stevens.cs549.hadoop.pagerank.PageRankDriver composite s3://cs549/input s3://cs549/output inter1 inter2 diff 10
\end{lstlisting}

\begin{table}[h]
    \caption{Spread of COVID-19 by Continent}
    \centering
    \begin{tabular}{|ll|}
    \hline
    Number of Reducers & Processing Time \\ \hline
    5                  & 13s             \\
    10                 & 18s             \\
    20                 & 40s             \\ \hline
    \end{tabular}
\end{table}

Increasing the number of reducers increases the processing time of the algorithm.


\newpage
\section{Running on EMR}

\begin{lstlisting}[language=Bash, caption={Custom JAR Command}]
edu.stevens.cs549.hadoop.pagerank.PageRankDriver composite s3://cs549/input s3://cs549/output inter1 inter2 diff 10
\end{lstlisting}

The algorithm took 23 minutes to run on a 5 machine cluster with 10 reducers. The following ranking was outputted: 

\begin{lstlisting}[caption={output.txt}]
    5302153:0	12810.69631667126
    84707:0	8159.113728956683
    88822:0	7886.093686178045
    1921890:0	7275.127835822817
    5300058:0	5826.635099830321
    81615:0	5014.404767519376
    1804986:0	4197.8888148045
    5535280:0	4164.226675136804
    896161:0	3769.910788409694
    5535664:0	3714.2571317056295
    79583:0	3583.7680798360816
    1601519:0	3488.3225964390367
    687324:0	3455.841896902911
    1948883:0	3364.344625704658
    5308545:0	3190.9223377001085
    505135:0	3064.802824618247
    1603276:0	2941.357165895597
    5596267:0	2914.369814878134
    2497500:0	2825.4558209203
    2995510:0	2730.416154609054
    1650573:0	2659.3656421983587
    2370447:0	2565.2363930365195
    77935:0	2528.8948762668074
    4141787:0	2407.816159087741
    3492254:0	2356.5909651517313
    2437900:0	2304.3565862362984
    2401294:0	2295.6349478790767
    4189168:0	2293.5300406199854
    687618:0	2224.083020041053
    3072654:0	2102.6401724186544
    434174:0	2102.335180035135
    3988566:0	2096.664388916008
    4015997:0	2018.9134163444628
    686242:0	2005.6101902332678
    4696900:0	1961.1958496038294
    76573:0	1960.9973826414164
    4351989:0	1959.317983917727
    478879:0	1904.298745200261
    3603437:0	1898.3236554574517
    5115901:0	1879.5875947888485
    2876077:0	1846.0542169601665
    1386743:0	1841.197756971188
    5492723:0	1780.7479241121116
    3997849:0	1712.6427307459228
    75323:0	1630.2723881913055
    3587465:0	1575.4630614468424
    4089591:0	1571.4228562480328
    181909:0	1553.487944478633
    4015913:0	1537.6157012671888
    3013310:0	1487.1735404348779    
\end{lstlisting}

\newpage
When trying to run more than 5 reducers or more than 5 clusters on the Amazon EMR service resulted in the following error: 

\begin{quote}
    Terminated with errorsThe request to create the EMR cluster or add EC2 instances to it failed. The number of vCPUs for instance type m5.xlarge exceeds the EC2 service quota for that type. Request a service quota increase for your AWS account or choose a different instance type and retry the request. 
    
    For more information, see https://docs.aws.amazon.com/console/elasticmapreduce/vcpu-limit
\end{quote}

I cannot find any information on Canvas about setting up EMR or addressing this issue. I asked a question on Piazza and awaiting for the reply at the time of submitting this assignment.

\end{document}